---
title       : Week4 Data Products Presentation
subtitle    : HTML Slides for R-Markdown
author      : Venkata
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Slide 1

Data products Final Assignment is about creating a shiny app that has some widgets and 
dynamic updates to the content on user data updates (Use of reactive function()).
I created a shiny app to display the Wages for different ages.

---

## Motion chart

Summary of the dataset.

```{r echo = F}
library(ISLR)
data(Wage)
summary(Wage)

```

---

##Plot between Wages and Ages.

```{r, result = 'asis', message=FALSE}
plot( Wage$age, Wage$wage, ylab = "Wages", xlab = "Age", data = Wage)
```

---

## Conclusion:

Shiny app is created to display the relationship between Wages and Ages. I used lineat regression model for this purpose.
On selecting the age, the respective Wage is plotted on the graph.






